Approximation as Differentiation

### 2025-05-06 appendix/notes/auto-diff.tex
Use const family notation.

For any map $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$ write $f_1$ for $\pi_1 \comp f$ and $f_2$ for
$\pi_2 \comp f$.

@@

Recall that the category $\Fam(\FinVect)$ is the Grothendieck construction $\Grothendieck{X}\Fam(X,
\FinVect)$. The functor $\Diff \hookrightarrow \Fam(\FinVect)$ which send objects $\RR^n$ to constant
families of tangent spaces $(\RR^n, \{\RR^n\}_{x \in \RR^n})$ and morphisms $f: \RR^m \to \RR^n \times (\RR^m
\linearto \RR^n)$ to pairs of differentiable functions $f_1: \RR^m \to \RR^n$ and constant families of linear
maps $f_2: \{\delta f_x: \RR^m \linearto \RR^n\}_{x \in \RR^m}$ exhibits $\Diff$ as equivalent to a full
subcategory of $\Fam(\FinVect)$.

For any $(f, \partial f): (\RR^m, \{\RR^m\}_{x \in \RR^m}) \to (\RR^n, \{\RR^n\}_{x \in \RR^n})$ and $(g,
\partial g): (\RR^n, \{\RR^n\}_{x \in \RR^n}) \to (\RR^k, \{\RR^k\}_{x \in \RR^k})$ in the image of that
functor, we have that for any $x \in \RR^m$:
\begin{itemize}
\item $\partial f_x: \RR^m \to \RR^n$;
\item $\reindex{\partial g}{f}_x = \partial g_{f(x)}: \RR^n \to \RR^k$
\end{itemize}

\noindent with the composition $(g, \partial g) \comp (f, \partial f) = (g \comp f, \reindex{\partial g}{f}
\comp \partial f): (\RR^m, \{\RR^m\}_{x \in \RR^m}) \to (\RR^k, \{\RR^k\}_{x \in \RR^k})$ corresponding
exactly to the chain rule, since $(\reindex{\partial g}{f} \comp \partial f)_x = {\partial g}_{f(x)} \comp
{\partial f}_x$.

>>>>

For any map $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$ define $f_1 = \pi_1 \comp f: \RR^m \to \RR^n$
and $f_2 = \pi_2 \comp f: \RR^m \to (\RR^m \linearto \RR^n)$.

@@

Recall that the category $\Fam(\FinVect)$ is the Grothendieck construction $\Grothendieck{X}\Fam(X,
\FinVect)$. The functor $\Diff \hookrightarrow \Fam(\FinVect)$ which send objects $\RR^n$ to constant families
of tangent spaces $(\RR^n, \const(\RR^n))$ and morphisms $f: \RR^m \to \RR^n \times (\RR^m \linearto
\RR^n)$ to pairs $(f_1, f_2)$ of differentiable functions $f_1: \RR^m \to \RR^n$ and families of linear maps
$f_2: \{{f_2}_x: \RR^m \linearto \RR^n\}_{x \in \RR^m}$ exhibits $\Diff$ as equivalent to a full subcategory
of $\Fam(\FinVect)$.

For any $(f, \partial f): (\RR^m, \const(\RR^m)) \to (\RR^n, \const(\RR^n))$ and $(g, \partial g): (\RR^n,
\const(\RR^n)) \to (\RR^k, \const(\RR^k))$ in that subcategory, we have that for any $x \in \RR^m$:
\begin{itemize}
\item $\partial f_x: \RR^m \to \RR^n$;
\item $\reindex{\partial g}{f}_x = \partial g_{f(x)}: \RR^n \to \RR^k$
\end{itemize}

\noindent The composition $(g, \partial g) \comp (f, \partial f) = (g \comp f, \reindex{\partial g}{f} \comp
\partial f): (\RR^m, \const(\RR^m)) \to (\RR^k, \const(\RR^k))$ corresponds exactly to the chain rule, since
$(\reindex{\partial g}{f} \comp \partial f)_x = {\partial g}_{f(x)} \comp {\partial f}_x$.
